COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-08-07 main.tex
Finish intro, outline sections

This work is organized in the following way.

In this study, we will examine the dynamical effects that give rise to collisions between planetesimals under the influence of an external giant planet. Near mean motion resonances (MMRs), the surface density and eccentricity dispersion of planetesimals becomes significantly altered \citep{2000Icar..143...45R, 2017ApJ...850..103B}. The effect that this has on the behavior of collisional grinding in these regions is not well understood. The way in which planetesimals move and interact in the vicinity of MMRs is extremely nonlinear and is best studied with N-body methods. Collision detection in an N-body simulation is extremely computationally expensive. So far, most studies of planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}. Also see \citep{2001A&A...373..683C}. The only exception to this are a series of N-body studies of a Jupiter sized planet embedded in a disk of colliding planetesimals \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}. In these simulations, the close proximity of the planetesimals to the planet produces a significant population of high eccentricity bodies, diluting the dynamical and collisional features near MMRs.

This paragraph is an outline of the paper

@@

\section{Simulations}\label{sec:sims}

Overview of ChaNGa and collision code

Talk about initial conditions, meant to be similar to case B in \citet{2000Icar..143...45R}.

@@

\section{Results}\label{sec:results}

>>>>

This work is organized in the following way. In section \ref{sec:dynamics} we provide an overview of the dynamics that drive the evolution of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:setup} we describe the N-body code we use and describe how we constructed the initial conditions for the two simulations that are run: one with a perturber on a circular orbit and one with an eccentric perturber. Section \ref{sec:results} goes on to explore the results of the two, with particular focus on the radial variation in the collision rates. In section \ref{sec:dust}, we use the positions of the collision events to construct a map of second generation dust emission, under the assumption that dust grains produced by collisions will immediately couple to the gas and circularize their orbits. Finally, we assess the observability of features in the dust emission due to mean motion resonances and conclude in section \ref{sec:discuss}.

\section{Collisions and Mean Motion Resonances} \label{sec:dynamics}

\section{Simulation Setup} \label{sec:setup}

\section{Results} \label{sec:results}

\section{Dust Emission} \label{sec:results}

\section{Summary and Discussion} \label{sec:discuss}

@@

@@
